---
title: "cross_validation"
author: "Martha Mulugeta"
date: "11/12/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

## Cross validation

Generate a dataset

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

Training and testing
anti_join -- give me everything that does not appear in the training dataset from the nonlin df for the testing dataset

```{r}
train_df = sample_frac(nonlin_df, size = .8)
test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

Fit three models of varying goodness 

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

Let's look at some fits

```{r}
##Fitting models based on training datasets
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
##Not a good fit; worst

train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
##This is a great fit; best

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
##Better than linear regression, which missed curves, but this is doing too much; great for this dataset, but wouldn't be for some dataset you haven't seen before; second best
```

```{r}
##Using the models made with the training datasets to predict the testing datasets; Smaller numbers are better than larger, but it is more relative than absolute
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
##Tells us how well at predicting the model is; always pick the model that predicts the testing dataset better, not modeling the training dataset
```

## Do this all using `modelr` package

```{r}
##Take in dataframe, want 20% in test df and 80% in training df, and run this 100 training-testing pairs and save them into df
cv_df = 
  crossv_mc(nonlin_df, 100) 
```

One note about resample...

```{r}
##Pull out training first training/testing split. Can pull the lists out individually and manipulate them
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble
```

```{r}
##Not a fundamental change; went from storing rows to storing the dataframes to allow us to fit models
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Try fitting the linear model to all of these...

```{r}
cv_df %>% 
  mutate(
    linear_mod = map(train, ~lm(y ~ x, data = .x)),
    smooth_mod = map(.x = train, ~gam(y ~s(x), data = .x)),
    wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x)),
    rmse_lin = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))      
```

Visualize this

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
##Pick smooth model based on this 

most of the time, choose the piece-wise linear model over the smooth because it is easier to interpret; although, both can be fairly similar. 

