---
title: "linear_models"
author: "Martha Mulugeta"
date: "11/7/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))


set.seed(1)
```

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Fit a first linear model! 
When you have categorial predictor, r organizes factors according to the order you have them in- Bronx becomes reference category automatically

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)
```

```{r}
fit 

summary(fit)
coef(fit)
summary(fit)$coef
```

tidy the results instead
```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)

##to more information than the broom tidy aside from the tibble; p-vale in glance corresponds to f statistic of whole model whereas tidy tells you for individual regression coefficient
fit %>% 
  broom::glance()
```

## Take a look at factors...
factor infreq puts categorical variables in order to how frequently they appear--most to least

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type)
  )
```

Refit the last model 

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit %>%
  broom::tidy()
```

## diagnostics
Added column for residuals using modelr::add_residuals; same for predictions, which is plugging in coefficient estimates into the equation

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = boro, y = resid)) +
  geom_violin() +
  ylim(-500, 500)

modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() 

modelr::add_predictions(nyc_airbnb, fit)
```

## nesting 
Does going up in one star change the price more in one boro than another? You will pay higher in Manhattan for a one star increase than you would in the other boroughs; added in room type by boro as well

```{r}
fit_interaction = lm(price ~ stars * boro + room_type * boro, data = nyc_airbnb)

fit_interaction %>% 
  broom::tidy()
```

```{r}
nyc_airbnb %>% 
  filter(boro == "Brooklyn") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()
```

```{r}
nyc_airbnb %>%
  nest(data = -boro) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(boro, results) %>% 
  unnest(results)
```

Let's nest neighborhoods

```{r}
nyc_airbnb %>%
  filter(boro == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(neighborhood, results) %>% 
  unnest(results)
```

Save df as object before additional plotting 

```{r}
manhattan_nest_lm_results = 
  nyc_airbnb %>%
  filter(boro == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(neighborhood, results) %>% 
  unnest(results)

manhattan_nest_lm_results %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```

```{r}
nyc_airbnb %>% 
  filter(neighborhood == "NoHo", room_type == "Shared room")
```

